Computing Exact Restricted Isometry Constants via Mixed Integer Semidefinite Programming

### 2016-03-22 RIP-MISDP-Paper/IEEE_RIP-MISDP.tex
branch and bound -> branch-and-bound and updated table

In order to successfully apply branch and bound to \eqref{MISDP}, it is
important to use strong semidefinite relaxations for fractional $z$
variables. To this end, we can use the following strengthening of the
constraints $-z_j \leq X_{ij} \leq z_j$.

@@

\noindent
In this section we demonstrate the applicability of the proposed MISDP-formulation and use it to
assess the quality of the relaxations proposed in~\cite{Asp08} and~\cite{Asp07}.
For solving the mixed integer semidefinite programs, we use the MISDP solver SCIP-SDP~\cite{SCIP-SDP,GalPU16},
originally developed in~\cite{Mar13} and~\cite{MS12}. It combines the
branch and bound framework SCIP 3.2.1 \cite{SCIP} with 
interior-point SDP-solvers, in our case SDPA~7.3.8~\cite{SDPA6,SDPA7}.

@@

\newpage
\appendix{ \input{tables/matrixList}}

>>>>

In order to successfully apply branch-and-bound to \eqref{MISDP}, it is
important to use strong semidefinite relaxations for fractional $z$
variables. To this end, we can use the following strengthening of the
constraints $-z_j \leq X_{ij} \leq z_j$.

@@

\noindent
In this section we demonstrate the applicability of the proposed MISDP-formulation and use it to
assess the quality of the relaxations proposed in~\cite{Asp08} and~\cite{Asp07}.
For solving the mixed integer semidefinite programs, we use the MISDP solver SCIP-SDP~\cite{SCIP-SDP,GalPU16},
originally developed in~\cite{Mar13} and~\cite{MS12}. It combines the
branch-and-bound framework SCIP 3.2.1 \cite{SCIP} with 
interior-point SDP-solvers, in our case SDPA~7.3.8~\cite{SDPA6,SDPA7}.

@@

\newpage
\appendix{\input{tables/matrixList}}
